\subsubsection{GPS Feeder}
\label{GPSFeeder}
The GPS Feeder, {\it gpsFeeder.py}, updates the watcher daemon on the current location of a single node on the test bed. It is usually run on the test node itself, thus 
every test node updates its own location. The GPS is read from a locally running {\it gpsd} process. (See {\verb http://gpsd.berlios.de} for 
details of {\it gpsd}.) The watcher GPS Feeder can be found at ./src/clients/gpsFeeder. It consists of a python script that uses the 
python interface exported by {\it gpsd}. Once a second, it retrieves the curent GPS location of the local node and makes a system call via the shell to sendGPSMessage ~\ref{sendGPSMessage}. (Since it
calls {\it sendGPSMessage}, {\it sendGPSMessage} must be in the PATH of the shell in which gpsFeeder is launched. 
\\\\
Usage: 
{\tt gpsFeeder -s server}
\\\\
Required Arguments:
\begin{itemize}
\item {\tt -s,--server=address|name}, The address or name of the node running watcherd.
\end{itemize}
Example:
\begin{itemize}
\item Run the gpsFeeder to give current location information to the watcher daemon once a second and save the output as a log to {\tt /var/log/gpsFeeder.log}.
    
{\tt gpsFeeder.py -s glory 2>\&1 /var/log/gpsFeeder.log}
\end{itemize}

Note: the {\it emane} system uses the gpsd from gpsd.berlios.de and this is the daemon that the gps feeder supports. There is an older {\it gpsDaemon} that supports a {\it MANE} environment, but that 
is not supported directly by this watcher system release. Use the unsupported {\it gpsDaemon} and the auxillary program {\it watcherHierarchyClient} (see page \pageref{watcherHierarchyClient}) for {\it MANE} support in this release 
of the watcher system.

There are plans to create a global GPS Feeder that would feed all location information to the watcher daemon directly in order to cut down on network traffic, which 
would be very useful once the watcher is run on a system with hundreds or thousands of nodes. But these are still just plans. 

