\newpage
\label{sendNodePropertiesMessage}
\subsubsection{sendNodePropertiesMessage}
{\bf sendNodePropertiesMessage} is a test node command line program that sends a NodePropertiesMessage message to the watcher daemon, specifing that a node property should change. 
\\\\
{\tt
        Usage: sendNodePropertiesMessage [args]
        Args:
           -s, --server=address        The address of the node running watcherd.

        Optional args:
            -n, --node=address          The node to modify, if empty the local node's address is used.
            -l, --layer=layer           The layer to apply these properties to. string, e.g. "hierachy". 
            -a, --shape=shape           The shape to make the node. One of: circle, triangle, square, torus, teapot.
            -e, --effect=effect         The effect to apply to the node, one of: flash, spin, sparkle.
            This agrument can be used multiple times. Not all GUIs support all effects.
            -P, --property=prop         Tell the daemon that this node has a certain property, one of
            leafnode, neighborhoor, regional, root, attacker, victim. This argument can be used
            more than once.
            -c, --color=color           Set the node's color to color. Color can be string, e.g. "blue", or 
            hex RRGGBBAA (red, green, blue, alpha) value, "0xff00ff64"
            -z, --size=float            How large (or small) to make the node relative to other nodes.
            -T, --timestamp=ms          Optionally specify a timestamp for this event
            -r, --logProps              log.properties file, which controls logging for this program
                                        Default value is sendMessage.log.properties.
            -h, --help                  Show this message
}

Examples:
