\newpage
\label{sendLabelMessage}
\subsubsection{sendLabelMessage}
{\bf sendLabelMessage} is a test node command line program that sends a watcher::event::LabelMessage message to the watcher daemon, specifing that a label should be attached to the specified node (or float if given coords).

If address is specified, the label will attach to the node with that address. If cooridinates are
specified, the label will float at those coordinates. The node address takes precedence. If neither
option is specified, the label will attach to the node from which the message saw sent.
\\\\
Usage: 
{\tt sendLabelMessage -s server -l label [optional args]}
\\\\
Required Arguments:
\begin{itemize}
\item {\tt -l, --label=text}, The text of the label
\item {\tt -s, --server=address}, The address|name of the node running watcherd, the server.
\end{itemize}
Optional args:
\begin{itemize}
\item {\tt -n, --node=address}, The node to change color, if empty the local node's address is used
\item {\tt -x, --latitude=coord}        The latitude to float the node at.
\item {\tt -y, --longitude=coord}       The longitude to float the node at.
\item {\tt -z, --altitiude=coord}       The altitude to float the node at.
\item {\tt -t, --fontSize=size}         The font size of the label
\item {\tt -f, --foreground=color}      The foreground color of the label. Can be ROYGBIV or RGBA format, string or hex value.
\item {\tt -b, --background=color}      The background color of the label. Can be ROYGBIV or RGBA format, string or hex value.
\item {\tt -e, --expiration=seconds}    How long in millisecond to diplay the label
\item {\tt -r, --remove}                Remove the label if it is attached
\item {\tt -L, --layer=layer}           Which layer the label is part of. Default is "Physcial".
\item {\tt -x, --expiration=seconds}, How long in seconds to change the color. 0==forever
\item {\tt -p, --logProps}, log.properties file, which controls logging for this program
\item {\tt -h, --help}, Show help message
\end{itemize}
Examples:
\begin{itemize}
\item sendLabelMessage -s glory -n 192.168.1.102 -l "Correlation Layer" -e 1500 -f red -b green -L Correlation
\item sendLabelMessage -s glory -n 192.168.1.102 -l "Physical Layer" -e 1500 -L Physical
\item sendLabelMessage -s glory -n 192.168.1.104 -l "Attack Detected" -f yellow -b blue -L Physical 
\end{itemize}

